% this file is part of demo thesis in English,
% the main TeX file should be `bachelor.tex` or `master.tex` in the parent directory.

\chapter{QUICK START}

Welcome to \nuaathesis,
a \LaTeX{} thesis template with English support for foreign language college and/or international students.
We assume that you are familiar with writing articles in \LaTeX.

The source code for this template is hosted on \url{https://github.com/nuaatug/nuaathesis},
feedback, issues and pull requests are always welcomed.

\section{Setup \LaTeX{} Environment}

\nuaathesis{} requires some packages which are not included in basic/minimum \LaTeX{} installation.
Here are some tips to install the depended packages:

If you are using the \TeX~Live from your system distribution,
please install the following \TeX~Live collections:
\verb|langchinese, latexextra, science, pictures, fontsextra|.

If you are using the \TeX~Live installed from \url{https://www.tug.org/texlive/},
\begin{enumerate}
  \item verify your \TeX~Live installation by executing: \verb|tlmgr --help|,
  make sure it has long, pages of output.
  \item go to the \verb|.ci| directory (may be hidden),
  run \verb|install.bat| (Windows) or \verb|install.sh| (others).
  For Windows users, the script might fail if your system doesn't have PowerShell.
  If the script doesn't work, install the texlive packages listed in \verb|.ci/texlive.pkgs| manually.
\end{enumerate}

If you are using Mik\TeX,
chances are that the dependencies will be installed automatically when you compile the document.
Good luck \verb|:)|

For Windows users, due to the \CTeX's assumption, you should either
\begin{itemize}
  \item install simplified Chinese fonts on Windows, or
  \item specify document option \verb|fontset=fandol| or any other Chinese fonts in your thesis
\end{itemize}

\section{Compile Template}

Run \verb|build.bat| (Windows) or \verb|build.sh| (others),
it will extract the document class and build the document.

Note:
if simplified Chinese fonts are not installed on Windows,
the document \texttt{nuaathesis.pdf} might fail to build,
but the document class \texttt{nuaathesis.cls} should have been extracted.

\section{Compile Thesis}

Before compiling the thesis,
please make sure that the working directory contains following files/directories:
\begin{itemize}
  \item \verb|nuaathesis.cls|: document class;
  \item \verb|nuaathesis.bst|: biber style;
  \item \verb|logo/|: folder, contains some figures for cover and header.
\end{itemize}
If any of them is missing, please copy it from the root directory of the template.

There are a bunch of methods to compile a \LaTeX{} document,
assuming your thesis is called \verb|master.tex|
\begin{itemize}
\item the recommended compiling command is
\begin{shell}
latexmk -xelatex master
\end{shell}
\item the regular, decoupled compiling commands are
\begin{shell}
xelatex master
bibtex master
xelatex master
xelatex master
\end{shell}
\item you could replace \verb|xelatex| with any other \LaTeX{} engines supported by \CTeX,
but \XeLaTeX{} works best with Chinese document,
and we don't test compatibility with other \LaTeX{} engines except \XeLaTeX.
\end{itemize}

\section{Write/modify Thesis}

This document is also written with \nuaathesis,
why not adapt it into your thesis and save time for starting from scratch?
Here is the list of files that you need to modify:
\begin{itemize}
  \item \verb|master.tex|: the main document
  \item \verb|global.tex|: basic information for cover and abstract, import packages, define macros
  \item \verb|content/|: main matters are here
  \item \verb|bib/|: biber database
\end{itemize}

\section{Disclamer}

This is UNOFFICIAL \LaTeX{} thesis template for NUAA.
Since format specification on English thesis has never been published,
nor has this template received official certification,
there is the risk that the thesis format might not be accepted.

The story is almost the same as the Chinese ones.
We do our best to match \nuaathesis{} with (the only Chinese) official Word template,
but we cannot provide any guarantee for the correct format.
